# Data transformation

## The Columns we chose

Since the original data are very dirty, we processed it first directly in excel and loaded it to R software for further processing.

```{r,warning=FALSE}
## packages loaded
library(readxl)
library(ggplot2)
library(tidyverse)
library(treemapify)
library(mi)
library(GGally)
library(gridExtra)
library(lubridate)
```

```{r}
## data loaded
airbnb_ny <- read_excel("./resource/airbnb_ny.xlsx")
```

```{r}
## data transformation
airbnb_new <- airbnb_ny %>% mutate(id = as.factor(id),host_id = as.factor(host_id))
```


```{r}
## missing value situation
colSums(is.na(airbnb_new)) %>% sort(decreasing = TRUE)
```

The brief understanding of the data is that there are 44187 airbnb houses collected in this dataset and 26 features are scraped which can be gathered into three main feature group, ie, house information, host information, evaluation information

House information (10 features): id, host_since, neighbourhood_group, latitude, longitude, room_type, accomodates, price, availability_30, availability_365

Host information (6 features): host_id, host_response_rate, host_acceptance_rate, host_listings_count, host_has_profile_pic, host_identity_verified.

Evaluation information (10 features): number_of_review, last_review, review_scores_rating, review_scores_accuracy, review_scores_cleanliness, review_scores_checkin, review_scores_communication, review_scores_location, review_scores_value, review_per_month


