# Data transformation

## The Columns We Chose From Listings.csv

After we downloaded the CSV file, we processed it first directly in excel as it is a great way to look for every column we had. We chose to keep: `id`,`host_id`,`host_since`,`host_response_rate`,`host_acceptance_rate`,	`host_listings_count`,	`host_has_profile_pic`,	`host_identity_verified`,	`neighbourhood_group`, `latitude`,	`longitude`,	`room_type`,	`accommodates`,	`price`,	`availability_30`,	`availability_365`,	`number_of_reviews`,	`last_review`,	`review_scores_rating`,	`review_scores_accuracy`,	`review_scores_cleanliness`,	`review_scores_checkin`,	`review_scores_communication`,	`review_scores_location`,	`review_scores_value`, and	`reviews_per_month` as these variables might be meaningful for our further analysis.


The brief understanding of the data is that there are 44187 Airbnb properties collected in this dataset and 26 features that we chose can be grouped into three feature groups: property information, host information, review information

Property information (10 features): `id`, `host_since`, `neighbourhood_group`, `latitude`, `longitude`, `room_type`, `accomodates`, `price`, `availability_30`, `availability_365`.

Host information (6 features): `host_id`, `host_response_rate`, `host_acceptance_rate`, `host_listings_count`, `host_has_profile_pic`, `host_identity_verified`.

Review information (10 features): `number_of_review`, `last_review`, `review_scores_rating`, `review_scores_accuracy`, `review_scores_cleanliness`, `review_scores_checkin`, `review_scores_communication`, `review_scores_location`, `review_scores_value`, `review_per_month`. 


## The year_bar Dataset

For the year_bar.csv file, we transform the hosts' data from the `host_since` column in order to see how Airbnb's hosting members grow over the years. We grouped the data by different boroughs then pivot the dataset wider so we have data filtered out for every year since 2008. 

```{r,warning=FALSE}
## packages loaded
library(tidyverse)

```

Let's see the whole picture of the dataset: 
```{r}
year_bar <- read_csv("./resource/year_bar.csv")
year_bar
```









