# Data transformation

## The Columns We Chose From Listings.csv

After we downloaded the CSV file, we processed it first directly in excel as it is a great way to look for every column we had. We chose to keep: `id`,`host_id`,`host_since`,`host_response_rate`,`host_acceptance_rate`,	`host_listings_count`,	`host_has_profile_pic`,	`host_identity_verified`,	`neighbourhood_group`, `latitude`,	`longitude`,	`room_type`,	`accommodates`,	`price`,	`availability_30`,	`availability_365`,	`number_of_reviews`,	`last_review`,	`review_scores_rating`,	`review_scores_accuracy`,	`review_scores_cleanliness`,	`review_scores_checkin`,	`review_scores_communication`,	`review_scores_location`,	`review_scores_value`, and	`reviews_per_month` as these variables might be meaningful for our further analysis.


The brief understanding of the data is that there are 44187 Airbnb properties collected in this dataset and 26 features that we chose can be grouped into three feature groups: property information, host information, review information

Property information (10 features): `id`, `host_since`, `neighbourhood_group`, `latitude`, `longitude`, `room_type`, `accomodates`, `price`, `availability_30`, `availability_365`.

Host information (6 features): `host_id`, `host_response_rate`, `host_acceptance_rate`, `host_listings_count`, `host_has_profile_pic`, `host_identity_verified`.

Review information (10 features): `number_of_review`, `last_review`, `review_scores_rating`, `review_scores_accuracy`, `review_scores_cleanliness`, `review_scores_checkin`, `review_scores_communication`, `review_scores_location`, `review_scores_value`, `review_per_month`. 


## The year_bar Dataset

For the year_bar.csv file, we transform the hosts' registration data from the `host_since` column in order to see how Airbnb's hosting members grow over the years. We grouped the data by different boroughs then pivot the dataset wider so we have data filtered out for every year since 2008. We will use this dataset for our interactive bar chart in part 6.

```{r,warning=FALSE}
## packages loaded
library(tidyverse)
library(readr)
library(tidyverse)
library(ggplot2)
library(readxl)
```

Let's see the dataset: 
```{r}
year_bar <- read_csv("./resource/year_bar.csv")
year_bar
```

## Data manipulation 
```{r}
airbnb_ny <- read_excel("./resource/airbnb_ny.xlsx")
```

To conduct further analysis and visualizations, we filtered the `price` variable into three levels "Expensive", "Medium", and "Budget". We define any property that has a price higher or equal to `$160` as an expensive Airbnb listing. The medium price level is from `$65` to `$159`. The budget properties are those cheaper than `$65`. Meanwhile, we also separated the `review_scores_rating` variable into three levels, "Excellent", "Poor", and "Good". The definition of an excellent property is that the listing received an overall score rating of 100. We defined the scores from 92 to 99 to be good review scores. Lastly, those properties that received a review rating of less than 92 are poor reviews.  We separated three levels of these two variables according to their interquartile ranges. 


Price: 
```{r}
quantile(as.numeric(airbnb_ny$price), probs=c(.25, .75), na.rm = TRUE)
ggplot(airbnb_ny,aes(price))+
  geom_boxplot(varwidth=TRUE)
```

Overall review scores:
```{r}
quantile(as.numeric(airbnb_ny$review_scores_rating), probs=c(.25, .75), na.rm = TRUE)

ggplot(airbnb_ny,aes(review_scores_rating))+
  geom_boxplot(varwidth=TRUE)
```







