# Missing values


We plot a vis_miss heat graph to investigate the missing patterns in variables that involved in following data analysis.


For missing row patterns, we observe that most of the rows don't have missing values. Majority of rows that with missing values only have missings in variable  .   


For missing column patterns, we find that there are 8 columns having missing values. Variable ```transit``` has the highest number of missing values, with about 17% of the value missing. Since “transit” is an entry that needs to be manually entered by property owners, we think the laziness of some owners lead to the missing values in ```transit```. Other 7 variables of ```comments```, ```location_scores```(denoted as "locatin_scrs" in the plot), ```checkin_scores```(denoted as "checkin_scrs" in the plot), ```communication_scores```(denoted as "cmmnctn_scrs" in the plot), ```clean_scores```,```accuracy_scores```(denoted as "accuracy_scrs" in the plot)  and ```review_scores```(denoted as "rvw_scores" in the plot) only have missing values in very few rows hence their missing distribution are not reflected in the bar graph on the bottom.


```{r,warning=FALSE}
## packages loaded
library(readxl)
library(ggplot2)
library(tidyverse)
library(treemapify)
library(mi)
library(GGally)
library(gridExtra)
library(lubridate)
library(ggalluvial)
library(scales)
library(naniar)
```


```{r}
## data loaded
airbnb_ny <- read_excel("./resource/airbnb_ny.xlsx")
```



```{r}
gg_miss_var(airbnb_ny)
```


```{r}
colSums(is.na(airbnb_ny)) %>%sort(decreasing =TRUE)
```







